%-------------------------
% One Page Optimized Resume (Rewritten for clarity, credibility, and impact)
%-------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[margin=0.5in, bottom=0.3in]{geometry}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\raggedbottom
\setlength{\tabcolsep}{0in}
\urlstyle{same}
\pdfgentounicode=1

\linespread{0.95}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\setlist[itemize]{itemsep=0.5pt, topsep=1pt}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small #3} & \textit{\small #4}
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \small\textbf{#1} & \small #2
  \end{tabular*}\vspace{-4pt}
}

\begin{document}

%----------HEADER----------
\begin{center}
  \textbf{\Huge \scshape Deepa Patel} \\ \vspace{2pt}
  \small
  +91 6386856939 $|$
  \href{mailto:pateldeepa017@gmail.com}{pateldeepa017@gmail.com} $|$
  Kanpur, India $|$
  \href{https://www.linkedin.com/in/deepa-patel-71678b293/}{LinkedIn} $|$
  \href{https://github.com/D-393Patel}{GitHub}
\end{center}

%----------SUMMARY----------
\section{Summary}
\begin{itemize}[leftmargin=0.15in,label={}]
\small{
\item Computer Science undergraduate with hands-on experience building backend APIs, automation workflows, and ML pipelines. Strong foundation in data structures, databases, and system design, with project experience across Node.js, PostgreSQL, Python, Docker, and MLOps tooling.
}
\end{itemize}

%----------EDUCATION----------
\section{Education}
\begin{itemize}[leftmargin=0.15in,label={}]
\resumeSubheading
{Pranveer Singh Institute of Technology}{Kanpur, India}
{B.Tech in Computer Science (AI \& ML) \;|\; CGPA: 8.89}{Aug 2023 -- Apr 2027}
\end{itemize}

%----------SKILLS----------
\section{Technical Skills}
\small
\textbf{Languages}: Java, Python, C, JavaScript, TypeScript \\
\textbf{Core CS}: Data Structures and Algorithms, Object-Oriented Programming, DBMS, Operating Systems \\
\textbf{Backend \& Web}: Node.js, Express.js, React.js, Next.js, REST APIs, HTML, CSS \\
\textbf{Databases}: PostgreSQL, MongoDB \\
\textbf{Cloud \& DevOps}: Docker, CI/CD, AWS (Basics) \\
\textbf{Tools}: Git, Linux/Unix, MLflow, DVC

%----------PROJECTS----------
\section{Projects}
\begin{itemize}[leftmargin=0.15in,label={}]

\resumeProjectHeading
{\textbf{Nodebase -- Workflow Automation Platform} $|$ \href{https://nodeflowz.vercel.app/login}{Live} $|$ \href{https://github.com/D-393Patel/nodebase}{Code}}
{Jan 2026 -- Mar 2026}
\begin{itemize}[leftmargin=0.25in]
\small{
\item Built backend services for an API-driven workflow platform using Node.js and PostgreSQL, supporting task execution, state management, and automation flows.
\item Implemented asynchronous job processing with retry and failure-handling logic to improve reliability for long-running tasks.
\item Optimized database queries and added indexing for frequently accessed workflow data, reducing lookup latency in heavier usage scenarios.
\item Added logging and monitoring hooks to help trace failures, debug issues faster, and improve service visibility during development.
}
\end{itemize}

\resumeProjectHeading
{\textbf{Sonique -- Real-Time Text-to-Speech Service} $|$ \href{https://sonique-production-c72f.up.railway.app/}{Live} $|$ \href{https://github.com/D-393Patel/Sonique}{Code}}
{Feb 2026 -- Mar 2026}
\begin{itemize}[leftmargin=0.25in]
\small{
\item Developed backend APIs for text-to-speech generation and audio delivery, focusing on responsive request handling and clean API design.
\item Built REST endpoints for processing text input, generating speech output, and serving audio results to client applications.
\item Improved request flow for concurrent usage by refining asynchronous handling and reducing unnecessary processing overhead.
}
\end{itemize}

\resumeProjectHeading
{\textbf{YouTube Comment Sentiment Analysis -- MLOps Pipeline} $|$ \href{https://github.com/D-393Patel/youtube-sentiment-mlops-pipeline}{Code}}
{Dec 2025 -- Jan 2026}
\begin{itemize}[leftmargin=0.25in]
\small{
\item Developed an end-to-end ML pipeline to preprocess YouTube comments, train sentiment models, and expose predictions through an API.
\item Processed 50K+ comments and used MLflow for experiment tracking and DVC for reproducible data and model workflows.
\item Containerized the inference pipeline with Docker to support consistent local setup and deployment.
}
\end{itemize}

\end{itemize}

%----------INTERNSHIP----------
\section{Internship}
\begin{itemize}[leftmargin=0.15in,label={}]
\resumeSubheading
{Infosys Springboard 6.0}{Nov 2025 -- Jan 2026}
{Project Intern}{}
\begin{itemize}[leftmargin=0.25in]
\small{
\item Built backend components for a price-tracking system using Python and Node.js to process product data and support comparison workflows.
\item Designed similarity-matching logic for product records, helping reduce redundant comparisons by 40\%.
\item Worked on performance-focused backend features with attention to efficient data processing, reliability, and maintainable service design.
\item Collaborated in an Agile team using Git-based workflows, code reviews, and iterative feature delivery.
}
\end{itemize}
\end{itemize}

%----------CERTIFICATIONS----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in]
\small{
\item Oracle Cloud Infrastructure 2025 Certified Generative AI Professional
\item Oracle Cloud Infrastructure 2025 Certified AI Foundations Associate
\item Introduction to C Programming, NPTEL
\item Agile Scrum in Practice, Infosys Springboard
}
\end{itemize}

%----------ACHIEVEMENTS----------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in,itemsep=0pt,topsep=0pt]
\small{
\item Solved 500+ problems across LeetCode, GeeksforGeeks, and HackerRank.
\item Vice President, Algo Club (PSIT), 2024--2025; helped organize 3+ campus hackathons for 100+ participants.
\item Semi-finalist, Build With India Hackathon; Level 3 Contributor, Hacktoberfest 2025.
\item Selected for Google Gen AI Exchange Program and Aspire Leadership Program (Harvard Business School Online).
\item Contributed to Women TechMakers technical workshops promoting inclusive technology learning.
}
\end{itemize}

\end{document}
